---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TimeTeller

<!-- badges: start -->
<!-- badges: end -->

TimeTeller is a supervised machine learning tool that analyses the local circadian clock as a system. It aims to estimate the circadian clock phase and the level of dysfunction from a single sample by modelling the multi-dimensional state of the clock. 

*TimeTeller* package implements the algorithm including methodology improvements and tools for visualisation.

## Installation

You can install the development version of TimeTeller from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("VadimVasilyev1994/TimeTeller")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(TimeTeller)
## basic example code
```


