---
title: "Basic_TimeTeller_Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic_TimeTeller_Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TimeTeller)
```

## Brief Introduction

This package builds on the work in [Original publication](https://www.biorxiv.org/content/10.1101/622050v2) and [Methodology](https://www.biorxiv.org/content/10.1101/2023.03.14.532177v1.full.pdf), which showed the potential of TimeTeller to act as an independent cancer biomarker in microarray data, extended the algorithm to RNA-seq data and performed extensive validation on some of the available mouse, baboon and human datasets.

TimeTeller is a supervised machine learning tool that analyses the local circadian clock as a system. It aims to estimate the circadian clock phase and the level of dysfunction from a single sample by modelling the multi-dimensional state of the clock. 

*TimeTeller* package implements the algorithm including methodology improvements and tools for visualisation.

## Standard Workflow

In this vignette we will look at two datasets: human oral mucosa and 

```{r load the data}
str(bjarn_data)
```
